Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
rephrasing to address comment, notes to self

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, their broad bandpasses
do not offer the same luxury of spectral resolution in dealing with line 
emission. Therefore, we must subtract estimates of the molecular line 
contamination from each \PLANCK~band in order to best isolate the thermal 
continuum we wish to characterize. The most prominent molecular line emission 
in the \PLANCK~bands of interest arises from the three lowest CO rotational
transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 GHz and 
J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 217 and 
353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

%We investigated the possibility of subtracting out CO emission 
%based on the template of \cite{planckco}. However, we found that the CO 
%emission rarely amounted to more than XX\% of the total intensity, and 
%following the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to 
%remove CO emission.

>>>>

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, the broad 
\PLANCK~bandpasses do not allow us to adopt the same appraoch as FDS99 in 
dealing with line emission. Instead, we must subtract estimates of the 
molecular line contamination from each \PLANCK~band in order to best isolate 
the thermal continuum we wish to characterize. The most prominent molecular 
line emission in the \PLANCK~bands of interest arises from the three lowest CO 
rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

% maybe a final sentence or two explaining that, to whatever extent
% CO line ratios vary over the sky and/or other molecules make a substantial
% contribution to the observed Planck intensities, our molecular emission
% correction will be insufficient
